Title

### 2012-05-03 inc/ms_model/ms_model.tex
expanded on the original model

Inserting \ref{eq:formal_evolution} into \ref{eq:gaussian_integral_dt} yields two integral terms, one related to the propagation of a non-charged Gaussian beam, the other adds the influence of the internal force due to Coulomb repulsion.
These terms will be denoted $K^{flow}$ and $K^{int}$ respectively.
\begin{equation} \label{eq:gaussian_integral_dt}
  \frac{d}{dt}(A^{-1})_{ij} = K^{flow}_{ij} + K^{int}_{ij}
\end{equation}
Collecting and expanding terms where possible gives these forms of the $K$ terms
\begin{gather}
  K^{flow}_{ij} \equiv -\frac{1}{N} \int u_i u_j \frac{\vec{p}}{m} \frac{\partial f}{\partial \vec{r}} d\vec{r} d\vec{p} \\
  K^{int}_{ij} \equiv \frac{1}{N} \int u_i u_j \frac{\partial f}{\partial \vec{p}} \frac{\partial \Phi(\vec{r};t)}{\partial \vec{r}} d\vec{r} d\vec{p} \\
  n(\vec{r};t) \equiv \int d\vec{p} f(\vec{r},\vec{p};t) 
    = \frac{N}{(2\pi)^{3/2} \sigma_{\smallT} \sqrt{\sigma_{z}}} \exp \left( -\frac{x^2+y^2}{2\sigma_{T}} - \frac{z^2}{2\sigma_{z}} \right) \\
  \begin{split}
    \Phi(\vec{r};t) \equiv & \int d\vecprime{r} V(\vec{r} - \vecprime{r}) n(\vecprime{r}; t) \\
    = & \frac{N}{(2\pi)^{3/2} \sigma_{\smallT} \sqrt{\sigma_{z}}} \int d\vecprime{r} V(\vec{r} - \vecprime{r}) \exp \left( -\frac{x^2+y^2}{2\sigma_{T}} - \frac{z^2}{2\sigma_{z}} \right)
  \end{split}
\end{gather}
Obviously the $K^{flow}$ term is far easier to evaluate
\begin{equation}
  K^{flow} = 
  \begin{pmatrix}
    k^{flow}_{\smallT} & 0 & 0 \\
    0 & k^{flow}_{\smallT} & 0 \\
    0 & 0 & k^{flow}_{z}
  \end{pmatrix}
  \quad \text{and} \quad
  k^{flow}_{\alpha} = 
  \begin{pmatrix}
    \dfrac{2\sigma_{\alpha}}{m} & \dfrac{1}{m} \left(\eta_{\alpha} + \dfrac{\gamma_{\alpha}^2}{\sigma_{\alpha}} \right) \\
    \dfrac{1}{m} \left(\eta_{\alpha} + \dfrac{\gamma_{\alpha}^2}{\sigma_{\alpha}} \right) & 0
  \end{pmatrix}
\end{equation}

@@

Not only is this an interesting result, but it can be both instructive and computationally useful.
We can rewrite \ref{eq:define_big_gamma} as $\eta_{\alpha} = \Gamma_{\alpha}^2 / \sigma_{\alpha}$ and substitute into \ref{eq:ag_original}.
\begin{subequations} \label{eq:ag_big_gamma}
\begin{gather}
  \frac{d\sigma_{\alpha}}{dt} = \frac{2\gamma_{\alpha}}{m} \\
  \frac{d\gamma_{\alpha}}{dt} = \frac{ \Gamma_{\alpha}^2 + \gamma_{\alpha}^2 }{\sigma_{\alpha} m}
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi)
\end{gather}
\end{subequations}
These four equations now contain all of the information previously contained in six, making this much less computationally intensive.
Further, now one can see that these $\Gamma$ constants can be thought of as some minimum/intrinsic action of the pulse. 
This will become more apparent when in future sections
%TODO include internal reference
it is shown that at the focal point of a lens, $\gamma_{\alpha}$ goes through zero.

>>>>

Inserting \ref{eq:formal_evolution} into \ref{eq:gaussian_integral_dt} yields two integral terms, one related to the propagation of a non-charged Gaussian beam, the other adds the influence of the internal force due to Coulomb repulsion.
These terms will be denoted $K^{flow}$ and $K^{int}$ respectively.
\begin{equation} \label{eq:gaussian_integral_dt}
  \frac{d}{dt}(A^{-1})_{ij} = K^{flow}_{ij} + K^{int}_{ij}
\end{equation}
Collecting and expanding terms where possible gives these forms of the $K$ terms
\begin{gather}
  K^{flow}_{ij} \equiv -\frac{1}{N} \int u_i u_j \frac{\vec{p}}{m} \frac{\partial f}{\partial \vec{r}} d\vec{r} d\vec{p} \\
  K^{int}_{ij} \equiv \frac{1}{N} \int u_i u_j \frac{\partial f}{\partial \vec{p}} \frac{\partial \Phi(\vec{r};t)}{\partial \vec{r}} d\vec{r} d\vec{p} \\
  n(\vec{r};t) \equiv \int d\vec{p} f(\vec{r},\vec{p};t) 
    = \frac{N}{(2\pi)^{3/2} \sigma_{\smallT} \sqrt{\sigma_{z}}} \exp \left( -\frac{x^2+y^2}{2\sigma_{T}} - \frac{z^2}{2\sigma_{z}} \right) \\
  \begin{split}
    \Phi(\vec{r};t) \equiv & \int d\vecprime{r} V(\vec{r} - \vecprime{r}) n(\vecprime{r}; t) \\
    = & \frac{N}{(2\pi)^{3/2} \sigma_{\smallT} \sqrt{\sigma_{z}}} \int d\vecprime{r} V(\vec{r} - \vecprime{r}) \exp \left( -\frac{x^2+y^2}{2\sigma_{T}} - \frac{z^2}{2\sigma_{z}} \right)
  \end{split}
\end{gather}
Obviously the $K^{flow}$ term is far easier to evaluate
\begin{equation}
  K^{flow} = 
  \begin{pmatrix}
    k^{flow}_{\smallT} & 0 & 0 \\
    0 & k^{flow}_{\smallT} & 0 \\
    0 & 0 & k^{flow}_{z}
  \end{pmatrix}
  \quad \text{and} \quad
  k^{flow}_{\alpha} = 
  \begin{pmatrix}
    \dfrac{2\sigma_{\alpha}}{m} & \dfrac{1}{m} \left(\eta_{\alpha} + \dfrac{\gamma_{\alpha}^2}{\sigma_{\alpha}} \right) \\
    \dfrac{1}{m} \left(\eta_{\alpha} + \dfrac{\gamma_{\alpha}^2}{\sigma_{\alpha}} \right) & 0
  \end{pmatrix}
\end{equation}
These analyses will be referred to while deriving the influence of external forces.
%TODO internal reference

The $K^{force}$ integrals, related to the internal force of the pulse's Coulombic repulsion, are far more complicated to evaluate.
For more information about the derivation, see \cite{michalik_analytic_2006}.
The final matrices are
\begin{equation}
  K^{force} = 
  \begin{pmatrix}
    k^{force}_{\smallT} & 0 & 0 \\
    0 & k^{force}_{\smallT} & 0 \\
    0 & 0 & k^{force}_{z}
  \end{pmatrix}
\end{equation}
where
\begin{equation}
  k^{force}_{\alpha} = 
  \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{2\pi^{1/2}\sigma_{\alpha}^{1/2}} L_{\alpha}(\xi)
  \begin{pmatrix}
    0 & 1 \\
    1 & \dfrac{2 \gamma_{\alpha}}{\sigma_{\alpha}}
  \end{pmatrix}
\end{equation}
The parameter $\xi$ is the ellipticity parameter, defined as
\begin{equation}
  \xi \equiv \sqrt{\dfrac{\sigma_{z}}{\sigma_{\smallT}}}
\end{equation}
Note that the original paper of Michalik and Sipe contained an error which incorrectly defined $\xi$; this was corrected in an erratum\cite{michalik_erratum:_2008}.
The family of $L$ functions are
\begin{gather}
  L_{\smallT}(\xi) = \frac{3}{2} \left( L(\xi) + \frac{\xi^2 L(\xi) - \xi}{ 1 - \xi^2 } \right) \\
  L_{z}(\xi) = \frac{ 3 \xi^2 }{ \xi^2 - 1} \left( \xi L(\xi) - 1 \right) \\
  L(\xi) = \frac{1}{2} \int_0^{\pi} \frac{1}{1+\xi\sin(\theta)} d\theta
\end{gather}

@@

Not only is this an interesting result, but it can be both instructive and computationally useful.
By rewriting \ref{eq:define_big_gamma} as $\eta_{\alpha} = \Gamma_{\alpha}^2 / \sigma_{\alpha}$ and substituting into \ref{eq:ag_original}.
\begin{subequations} \label{eq:ag_big_gamma}
\begin{gather}
  \frac{d\sigma_{\alpha}}{dt} = \frac{2\gamma_{\alpha}}{m} \\
  \frac{d\gamma_{\alpha}}{dt} = \frac{ \Gamma_{\alpha}^2 + \gamma_{\alpha}^2 }{\sigma_{\alpha} m}
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi)
\end{gather}
\end{subequations}
these four equations now contain all of the information previously contained in six. Having fewer equations, and fewer mathematical operations, makes this set of equations much less computationally intensive.
Further, now one can see that these $\Gamma$ constants can be thought of as some minimum/intrinsic action of the pulse. 
This will become more apparent when in future sections
%TODO include internal reference
it is shown that at the focal point of a lens, $\gamma_{\alpha}$ goes through zero.
